---
title: "MC Code Adapted for SxtA - Cleaned_up_notebook7b - qPCR linear regressions"
author: "Paul Den Uyl"
date: "2024-02-28"
output: html_document
---

```{r setup, include=FALSE}

#rm(list=ls())

#install.packages("rstan")
#install.packages("bayesplot")
#install.packages("brms")
#install.packages("mice")
library(rstan)
library(bayesplot)
library(brms)
library(readr)
library(dplyr)
library(pROC)
library(forcats)
library(mice)
library(VIM)
library(furrr)
library(tidyverse)

```

## Import Data and Format Dependent Variable (sxtA_Copies_mL) ##
```{r}

joined_data <- read_csv("data/Joined_qPCR_and_Water_Quality_data.csv",show_col_types = FALSE)

joined_data$Date_sameYear <- with(joined_data, update(joined_data$Date, year = 2000))         #Make new column with year 2000 for all dates, allows for month/day relationships to be examined ignoring year

joined_data <- joined_data %>% 
                          mutate(Date_core = if_else(Date_sameYear >= "2000-09-20" | Date_sameYear <= "2000-07-05", 0, 1)) %>%
                          mutate(Date_core = as.integer(Date_core))                           #Make grouping variable for samples within and outside of sxt detection dates

count_zero <- sum(joined_data$Date_core == 0, na.rm = TRUE)
count_one <- sum(joined_data$Date_core == 1, na.rm = TRUE)
count_zero #444 samples before and after first and last sxtA detection (metagenomic data)
count_one  #730 samples between first and last sxtA detection (metagenomic data)

#log10 transform dependent variable: sxtA_Copies_mL
joined_data$log10_sxtA_Copies_mL_BDL_Replaced<-log10(as.numeric(joined_data$sxtA_Copies_mL_BDL_Replaced))

#censor sxtA_Copies_mL, assign -1 to non-numeric values (NA and <BDL & <BQL)
joined_data$sxtA_Copies_mL_censored<-with(joined_data,ifelse(as.numeric(sxtA_Copies_Rxn)>=45&!(sxtA_Copies_Rxn == "BD")&!is.na(sxtA_Copies_Rxn),0,-1)) #Per Phytoxigene instructions, select 45 copies/rxn and above (Rao's code does 50, shown in sxtA_Copies_mL)

#check censored data 
  #View(joined_data %>%
  #          dplyr::select(sxtA_Copies_Rxn, sxtA_Copies_mL, log10_sxtA_Copies_mL_BDL_Replaced, sxtA_Copies_mL_censored))

```

#Sort independent data 
```{r}
###
#List of independent variables to consider:
#Ammonia
#Chlorophyll a
#Colored Dissolved Organic Material
#Dissolved Microcystin
#Dissolved N:P
#Dissolved Oxygen
#mcyE 
#Nitrate Nitrite
#Particulate Microcystin
#Particulate N:P
#Particulate Organic Carbon
#Particulate Organic Nitrogen
#Photosynthetically Active Radiation
#Phycocyanin
#Soluble Reactive Phosphorus
#Specific Conductivity
#Temperature
#Total Cyanobacteria
#Total Dissolved Phosphorus
#Total Phosphorus
#Total_Suspended_Solids
#Turbidity
#Volatile Suspended Solids
#Particulate N:P
#Dissolved N:P

###
#NOTE: For ease in determining distributions and other analyses, I'm going to remove all samples without qPCR data (never run) - wouldn't be considered in linear models anyway (because NA)
  #Keep only samples with qPCR data
   joined_data_sub <- joined_data %>% filter(!is.na(sxtA_Copies_Rxn)) 

#################### 
#Sample Temperature# 
#################### 
  #Combine Sample_Temperature_C & CTD_Temperature_C
  joined_data_sub$Comb_Temperature_C <- as.numeric(if_else(is.na(joined_data_sub$CTD_Temperature_C), joined_data_sub$Sample_Temperature_C, joined_data_sub$CTD_Temperature_C))

#######################
#Dissolved Microcystin#
#######################
  #Follow same imputation as performed by Casey for pMC
  joined_data_sub$Dissolved_Microcystin_ug_L_BDL_Replaced <- if_else(joined_data_sub$Dissolved_Microcystin_ug_L == "<0.1", as.numeric(0.1), as.numeric(joined_data_sub$Dissolved_Microcystin_ug_L))
  
#############
#Phycocyanin#
#############
  #Manual imputation, changing <value to value
  joined_data_sub <- joined_data_sub %>%
                      mutate(Extracted_Phycocyanin_ug_L_Replaced = if_else(grepl("<", Extracted_Phycocyanin_ug_L), 
                                                                           gsub("<", "", Extracted_Phycocyanin_ug_L), 
                                                                           Extracted_Phycocyanin_ug_L) %>% as.numeric()) 

#############################
#Soluble Reactive Phosphorus#
#############################
  #Manual imputation, changing <value to value
  joined_data_sub <- joined_data_sub %>%
                      mutate(Soluble_Reactive_Phosphorus_ug_P_L_Replaced = if_else(grepl("<", Soluble_Reactive_Phosphorus_ug_P_L), 
                                                                           gsub("<", "", Soluble_Reactive_Phosphorus_ug_P_L), 
                                                                           Soluble_Reactive_Phosphorus_ug_P_L) %>% as.numeric()) 
  
#########
#Ammonia#
#########
  #Manual imputation, changing <value to value
  joined_data_sub <- joined_data_sub %>%
                          mutate(Ammonia_ug_N_L_Replaced = if_else(grepl("<", Ammonia_ug_N_L), 
                                                                           gsub("<", "", Ammonia_ug_N_L), 
                                                                           Ammonia_ug_N_L) %>% as.numeric()) 

#################
#Nitrate+Nitrite#
#################
  #Manual imputation, changing <value to value
  joined_data_sub <- joined_data_sub %>%
                          mutate(Nitrate_Nitrite_mg_N_L_Replaced = if_else(grepl("<", `Nitrate_+_Nitrite_mg_N_L`), 
                                                                           gsub("<", "", `Nitrate_+_Nitrite_mg_N_L`), 
                                                                           `Nitrate_+_Nitrite_mg_N_L`) %>% as.numeric()) 

#####
#VSS#
#####
  joined_data_sub$Volatile_Suspended_Solids_mg_L <- as.numeric(joined_data_sub$Volatile_Suspended_Solids_mg_L)

############################
#Total Cyanobacteria - qPCR#
############################
  #log10 transform dependent variable: Total_Cyano_Copies_mL
  joined_data_sub$log10_Total_Cyano_Copies_mL<-log10(as.numeric(joined_data_sub$Total_Cyano_Copies_mL))

  #check what happened between log10 transformation
  #View(joined_data_sub %>%
  #        dplyr::select(Total_Cyano_Copies_mL, log10_Total_Cyano_Copies_mL))

#############
#mcyE - qPCR#
#############
  #log10 transform dependent variable: mcyE_Copies_mL
  joined_data_sub$log10_mcyE_Copies_mL_BDL_Replaced<-log10(as.numeric(joined_data_sub$mcyE_Copies_mL_BDL_Replaced))
  
#Note: currently considering values as-is BDL

#################
#ADD N:P parameters
#################
#Particulate N:P#
#################
  #Calculate, assign particulate N:P ratio - add to dataframe (df1b)
  joined_data_sub$Part_NP<-(joined_data_sub$Particulate_Organic_Nitrogen_mg_L / ((joined_data_sub$Total_Phosphorus_ug_P_L)-(joined_data_sub$Total_Dissolved_Phosphorus_ug_P_L)))
  
###############
#Dissolved N:P#
###############
  #Calculate, assign dissolved N:P ratio - add to dataframe (df1b)
  joined_data_sub$Diss_NP<-(((joined_data_sub$Nitrate_Nitrite_mg_N_L_Replaced) + (joined_data_sub$Ammonia_ug_N_L_Replaced)) / (joined_data_sub$Soluble_Reactive_Phosphorus_ug_P_L_Replaced))

###############
#Change -Inf in dataframe to 0 - caused by log10() of zero - Only one occurence in CTD_Photosynthetically_Active_Radiation_uE_m2_s
###############
joined_data_sub <- joined_data_sub %>%
  mutate(across(everything(), ~ ifelse(is.infinite(.) & . < 0, 0, .)))

```

#Impute using MICE
```{r}

data1 <- joined_data_sub %>% dplyr::select(log10_sxtA_Copies_mL_BDL_Replaced, sxtA_Copies_mL_censored, Date_core, Comb_Temperature_C, CTD_Specific_Conductivity_uS_cm, CTD_Dissolved_Oxygen_mg_L, CTD_Photosynthetically_Active_Radiation_uE_m2_s, Turbidity_NTU, Particulate_Microcystin_ug_L_BDL_Replaced, Dissolved_Microcystin_ug_L_BDL_Replaced, Extracted_Phycocyanin_ug_L_Replaced, Extracted_Chlorophyll_a_ug_L, Total_Phosphorus_ug_P_L, Total_Dissolved_Phosphorus_ug_P_L, Soluble_Reactive_Phosphorus_ug_P_L_Replaced, Ammonia_ug_N_L_Replaced, Nitrate_Nitrite_mg_N_L_Replaced, Particulate_Organic_Carbon_mg_L, Particulate_Organic_Nitrogen_mg_L, Colored_Dissolved_Organic_Material_absorbance_m1_at_400nm, Total_Suspended_Solids_mg_L, Volatile_Suspended_Solids_mg_L, log10_Total_Cyano_Copies_mL, log10_mcyE_Copies_mL_BDL_Replaced, Part_NP, Diss_NP)

# Specify variables to exclude from imputation
variables_to_ignore_1 <- c('Date_core', 'sxtA_Copies_mL_censored', 'Part_NP', 'Diss_NP')  

# Create a predictor matrix
pred1 <- make.predictorMatrix(data1)

# Set columns corresponding to variables_to_ignore to 0
pred1[, variables_to_ignore_1] <- 0

# Fit the GLM model using multiple imputations
imp <- mice::mice(data1, predictorMatrix = pred1, seed = 5, m = 20)
tbl1 <- complete(data = imp, 'long')

dim(data1)
dim(tbl1)
View(tbl1)
colSums(is.na(tbl1))

```

#Model 1
```{r}

parameters1 <- c("Comb_Temperature_C", "CTD_Specific_Conductivity_uS_cm", "CTD_Dissolved_Oxygen_mg_L", "CTD_Photosynthetically_Active_Radiation_uE_m2_s", "Turbidity_NTU", "Particulate_Microcystin_ug_L_BDL_Replaced", "Dissolved_Microcystin_ug_L_BDL_Replaced", "Extracted_Phycocyanin_ug_L_Replaced", "Extracted_Chlorophyll_a_ug_L", "Total_Phosphorus_ug_P_L", "Total_Dissolved_Phosphorus_ug_P_L", "Soluble_Reactive_Phosphorus_ug_P_L_Replaced", "Ammonia_ug_N_L_Replaced", "Nitrate_Nitrite_mg_N_L_Replaced", "Particulate_Organic_Carbon_mg_L", "Particulate_Organic_Nitrogen_mg_L", "Colored_Dissolved_Organic_Material_absorbance_m1_at_400nm", "Total_Suspended_Solids_mg_L", "Volatile_Suspended_Solids_mg_L", "log10_Total_Cyano_Copies_mL", "log10_mcyE_Copies_mL_BDL_Replaced", "Part_NP", "Diss_NP")

fit_list <- list()  # Initialize an empty list to store the models
model1 <- list( ) # Initialize an empty list to store combined models
loo_auto <- list()  # Initialize an empty list to store LOO scores
df <- tibble()      # Initialize an empty dataframe for final table results

# prevent pop-up windows/questions
options(buildtools.check = function(action) TRUE)

# Run fit on loop - not combining (combine = FALSE), so that you can extract the LOO for each run later, combined using combined_models()
for (param in parameters1) {
  # Construct the formula dynamically
  formula <- formula(paste("log10_sxtA_Copies_mL_BDL_Replaced | cens(sxtA_Copies_mL_censored) ~", param))
  
  # Run brm_multiple 
  fit_imp <- brm_multiple(formula, data = imp, chains = 4, warmup = 1000, iter = 2000, combine = FALSE)
  
  # Store the individual model in the list (backup)
  fit_list[[param]] <- fit_imp
  
  # Combine the model into object
  model1[[param]] <- combine_models(mlist = fit_imp, check_data = FALSE)

  # Get LOO for the combined model
  loo_auto[[param]] <- brms::loo(model1[[param]])

#Compile:
#Intercept: Estimate, Estimate Error, l-95% CI, u-95% CI, Rhat, Bulk_ESS, Tail_ESS
#Parameter: Estimate, Estimate Error, l-95% CI, u-95% CI, Rhat, Bulk_ESS, Tail_ESS
#R-squared

#Generate summary (for loop)
summary_result <- summary(model1[[param]])
r2 <- bayes_R2(model1[[param]])
# Extract R-squared value
param_r2 <- r2[1]

# Extract model results
fixed_effects_matrix <- summary_result$fixed

# Convert the fixed effects to a tibble
fixed_effects <- as_tibble(fixed_effects_matrix)

# Add the parameter names as a new column
fixed_effects <- fixed_effects %>%
  add_column(Parameter = param,
             Row = rownames(fixed_effects_matrix), .before = 1,
             R_squared = param_r2,
             Model_formula = paste("log10_sxtA_Copies_mL_BDL_Replaced | cens(sxtA_Copies_mL_censored) ~", param))

df <- bind_rows(df, fixed_effects)

}

model1_output <- print(df) %>%
                        arrange(-R_squared)
View(model1_output)
#Save objects
saveRDS(model1, file="qPCR/model1_June12_24.RData")
saveRDS(loo_auto, file="qPCR/loo_auto_model1_June12_24.RData")
write_csv(model1_output, "qPCR/model1_output_June12_24.csv")
#This concludes the first test of linear models, if rhat >1.01, consider transforming fixed variable and redo below
model1_output <- read_csv("qPCR/model1_output_June12_24.csv")
model1_read <- readRDS("qPCR/model1_June12_24.RData")
model1_temp_plot <- plot(brms::conditional_effects(model1_read[["Comb_Temperature_C"]]), points=TRUE)

model1_temp_plot_print <- model1_temp_plot[[1]] +
  geom_hline(yintercept = log10(45), linetype = "dashed", color = "red") +
  ylim(-7.5, 5)

# Save as PDF
#ggsave("qPCR/model1_temp_plot.pdf", plot = model1_temp_plot_print, width = 10, height = 6)

#################
#model1b
#################
#filter results with rhat 1.01 or greater
model1_output_RhatCutoff <- model1_output %>%
                                filter(Rhat >= 1.01) %>%
                                dplyr::select(Parameter, Rhat) %>%
                                distinct(Parameter)

#identify parameters in Model 1 that had an rhat >=1.01.
parameters1b_rhatcutoff <- model1_output_RhatCutoff$Parameter

# Transform (log10()) parameters with rhat >= 1.01 in the MICE object
imp1b <- imp  # Copy the mice object to preserve the original
tbl1b_long <- complete(data = imp1b, 'long', include=TRUE) # Convert to long form

# Generate new long transformed variables
for(param in parameters1b_rhatcutoff){
  param_name <- as.character(param)
  tbl1b_long[[paste0("log10_", param_name)]] <- log10(tbl1b_long[[param_name]])
}

tbl1b_long <- tbl1b_long %>%
  mutate(across(everything(), ~ ifelse(is.infinite(.) & . < 0, 0, .)))

# Convert back to Mids
imp1b_short <- as.mids(tbl1b_long)

# Make parameters1b list for Model1b
# Step 2: Identify new items from column names of tbl1b_long that are not in parameters1, as well as other relevant parameters
parameters1b <- setdiff(colnames(tbl1b_long), c(parameters1, "Date_core", "sxtA_Copies_mL_censored", "log10_sxtA_Copies_mL_BDL_Replaced", ".imp", ".id"))

fit_list1b <- list()  # Initialize an empty list to store the models
model1b <- list() # Initialize an empty list to store combined models
loo_auto1b <- list()  # Initialize an empty list to store LOO scores
model1b_output_bind <- tibble()      # Initialize an empty dataframe for final table results

# prevent pop-up windows/questions
options(buildtools.check = function(action) TRUE)

# Run fit on loop - not combining (combine = FALSE), so that you can extract the LOO for each run later, combined using combined_models()
for (param in parameters1b) {
  # Construct the formula dynamically
  formula1b <- formula(paste("log10_sxtA_Copies_mL_BDL_Replaced | cens(sxtA_Copies_mL_censored) ~", param))
  
  # Run brm_multiple 
  fit_imp1b <- brm_multiple(formula1b, data = imp1b_short, chains = 4, warmup = 1000, iter = 2000, combine = FALSE)
  
  # Store the individual model in the list (backup)
  fit_list1b[[param]] <- fit_imp1b
  
  # Combine the model into object
  model1b[[param]] <- combine_models(mlist = fit_imp1b, check_data = FALSE)

  # Get LOO for the combined model
  loo_auto1b[[param]] <- brms::loo(model1b[[param]])

#Compile:
#Intercept: Estimate, Estimate Error, l-95% CI, u-95% CI, Rhat, Bulk_ESS, Tail_ESS
#Parameter: Estimate, Estimate Error, l-95% CI, u-95% CI, Rhat, Bulk_ESS, Tail_ESS
#R-squared

#Generate summary (for loop)
summary_result1b <- summary(model1b[[param]])
r2 <- bayes_R2(model1b[[param]])
# Extract R-squared value
param_r2 <- r2[1]

# Extract model results
fixed_effects_matrix <- summary_result1b$fixed

# Convert the fixed effects to a tibble
fixed_effects <- as_tibble(fixed_effects_matrix)

# Add the parameter names as a new column
fixed_effects <- fixed_effects %>%
  add_column(Parameter = param,
             Row = rownames(fixed_effects_matrix), .before = 1,
             R_squared = param_r2,
             Model_formula = paste("log10_sxtA_Copies_mL_BDL_Replaced | cens(sxtA_Copies_mL_censored) ~", param))

model1b_output_bind <- bind_rows(model1b_output_bind, fixed_effects)

}

# View the final dataframe
model1b_output <- print(model1b_output_bind) %>%
                        arrange(-R_squared)

#Save objects
saveRDS(model1b, file="qPCR/model1b_June12_24.RData")
saveRDS(loo_auto1b, file="qPCR/loo_auto1b_June12_24.RData")
write_csv(model1b_output, "qPCR/model1b_output_June12_24.csv")
#This concludes the second iteration of linear models, once again if rhat >1.01
model1b_output <- read_csv("qPCR/model1b_output_June12_24.csv")
model1b_read <- readRDS("qPCR/model1b_June12_24.RData")
model1b_ammon_plot <- plot(brms::conditional_effects(model1b_read[["log10_Ammonia_ug_N_L_Replaced"]]), points=TRUE)

model1b_ammon_plot_print <- model1b_ammon_plot[[1]] +
  geom_hline(yintercept = log10(45), linetype = "dashed", color = "red") +
  ylim(-7.5, 5)

# Save as PDF
#ggsave("qPCR/model1b_ammon_plot.pdf", plot = model1b_ammon_plot_print, width = 10, height = 6)

model1_temp_plot_print
model1b_ammon_plot_print

library(ggpubr)
model1_1b_temp_ammon_plot <- ggarrange(model1_temp_plot_print, model1b_ammon_plot_print)

# Save merged plot as PDF
ggsave("qPCR/model1_1b_temp_ammon_plot.pdf", plot = model1_1b_temp_ammon_plot, width = 20, height = 6)


#BIND RESULTS AND MOVE ON!
model1all_output <- bind_rows(model1_output, model1b_output)
View(model1all_output %>%
       dplyr::filter(Rhat <= 1.01))

```

#Model1c - Now add grouping variable (July 6 to September 19 and outside of dates)
```{r}
fit_list1c <- list()  # Initialize an empty list to store the models
model1c <- list() # Initialize an empty list to store combined models
loo_auto1c <- list()  # Initialize an empty list to store LOO scores
model1c_output_bind <- tibble()      # Initialize an empty dataframe for final table results

combined_parameters <- c(parameters1[!(parameters1 %in% parameters1b_rhatcutoff)], parameters1b) 

# prevent pop-up windows/questions
options(buildtools.check = function(action) TRUE)

# Run fit on loop - not combining (combine = FALSE), so that you can extract the LOO for each run later, combined using combined_models()
for (param in combined_parameters) {
  # Construct the formula dynamically
  formula1c <- formula(paste("log10_sxtA_Copies_mL_BDL_Replaced | cens(sxtA_Copies_mL_censored) ~", param, "+ (1 +", param, "| Date_core)"))
  
  # Run brm_multiple 
  fit_imp1c <- brm_multiple(formula1c, data = imp1b_short, chains = 4, warmup = 1000, iter = 2000, combine = FALSE)
  
  # Store the individual model in the list (backup)
  fit_list1c[[param]] <- fit_imp1c
  
  # Combine the model into object
  model1c[[param]] <- combine_models(mlist = fit_imp1c, check_data = FALSE)

  # Get LOO for the combined model
  loo_auto1c[[param]] <- brms::loo(model1c[[param]])

#Compile:
#Intercept: Estimate, Estimate Error, l-95% CI, u-95% CI, Rhat, Bulk_ESS, Tail_ESS
#Parameter: Estimate, Estimate Error, l-95% CI, u-95% CI, Rhat, Bulk_ESS, Tail_ESS
#R-squared

#Generate summary (for loop)
summary_result1c <- summary(model1c[[param]])
r2 <- bayes_R2(model1c[[param]])
# Extract R-squared value
param_r2 <- r2[1]

# Extract model results
fixed_effects_matrix <- summary_result1c$fixed

# Convert the fixed effects to a tibble
fixed_effects <- as_tibble(fixed_effects_matrix)

# Add the parameter names as a new column
fixed_effects <- fixed_effects %>%
  add_column(Parameter = param,
             Row = rownames(fixed_effects_matrix), .before = 1,
             R_squared = param_r2,
             Model_formula = paste("log10_sxtA_Copies_mL_BDL_Replaced | cens(sxtA_Copies_mL_censored) ~", param, "+ (1 +", param, "| Date_core)"))

model1c_output_bind <- bind_rows(model1c_output_bind, fixed_effects)

}

# View the final dataframe
model1c_output <- print(model1c_output_bind) %>%
                        arrange(-R_squared)

#Save objects
saveRDS(model1c, file="qPCR/model1c_June13_24.RData")
saveRDS(loo_auto1c, file="qPCR/loo_auto1c_June13_24.RData")
write_csv(model1c_output, "qPCR/model1c_output_June13_24.csv")
#This concludes the second iteration of linear models, once again if rhat >1.01
model1c_output <- read_csv("qPCR/model1c_output_June13_24.csv")

View(model1c_output)
```

###
###Model2: Let's do loop for (+) two predictors - MATRIX!
###
```{r}
#Select best parameters
parameters_model2 <- c("Comb_Temperature_C", "log10_Ammonia_ug_N_L_Replaced")

fit_list2 <- list()  # Initialize an empty list to store the models
model2 <- list() # Initialize an empty list to store combined models
loo_auto2 <- list()  # Initialize an empty list to store LOO scores
model2_output_bind <- tibble()      # Initialize an empty dataframe for final table results

# prevent pop-up windows/questions
options(buildtools.check = function(action) TRUE)

# Run fit on loop - not combining (combine = FALSE), so that you can extract the LOO for each run later, combined using combined_models()
for (param in parameters_model2) {
for (param2 in combined_parameters) {
  # Construct the formula dynamically
  formula2 <- formula(paste("log10_sxtA_Copies_mL_BDL_Replaced | cens(sxtA_Copies_mL_censored) ~", param, "+", param2))
  
  # Run brm_multiple 
  fit_imp2 <- brm_multiple(formula2, data = imp1b_short, chains = 4, warmup = 1000, iter = 2000, combine = FALSE)
  
  # Store the individual model in the list (backup)
  fit_list2[[paste(param, "+", param2)]] <- fit_imp2
  
  # Combine the model into object
  model2[[paste(param, "+", param2)]] <- combine_models(mlist = fit_imp2, check_data = FALSE)

  # Get LOO for the combined model
  loo_auto2[[paste(param, "+", param2)]] <- brms::loo(model2[[paste(param, "+", param2)]])

#Compile:
#Intercept: Estimate, Estimate Error, l-95% CI, u-95% CI, Rhat, Bulk_ESS, Tail_ESS
#Parameter: Estimate, Estimate Error, l-95% CI, u-95% CI, Rhat, Bulk_ESS, Tail_ESS
#R-squared

#Generate summary (for loop)
summary_result2 <- summary(model2[[paste(param, "+", param2)]])
r2 <- bayes_R2(model2[[paste(param, "+", param2)]])
# Extract R-squared value
param_r2 <- r2[1]

# Extract model results
fixed_effects_matrix <- summary_result2$fixed

# Convert the fixed effects to a tibble
fixed_effects <- as_tibble(fixed_effects_matrix)

# Add the parameter names as a new column
fixed_effects <- fixed_effects %>%
  add_column(Parameter = paste(param, "+", param2),
             Row = rownames(fixed_effects_matrix), .before = 1,
             R_squared = param_r2,
             Model_formula = paste("log10_sxtA_Copies_mL_BDL_Replaced | cens(sxtA_Copies_mL_censored) ~", param, "+", param2))

model2_output_bind <- bind_rows(model2_output_bind, fixed_effects)

}
}

# View the final dataframe
model2_output <- print(model2_output_bind) %>%
                        arrange(-R_squared)

#Save objects
saveRDS(model2, file="qPCR/model2_June17_24.RData")
saveRDS(loo_auto2, file="qPCR/loo_auto2_June17_24.RData")
write_csv(model2_output, "qPCR/model2_output_June17_24.csv")
#This concludes the second iteration of linear models, once again if rhat >1.01
model2_output <- read_csv("qPCR/model2_output_June17_24.csv")
model2_read <- readRDS("qPCR/model2_June17_24.RData")
model2_ammon_temp_plot <- plot(conditional_effects(model2_read[["log10_Ammonia_ug_N_L_Replaced + Comb_Temperature_C"]]), points=TRUE)
model2_ammon_temp_plot

View(model2_output)

```
###
#Model3: Let's do loop for interaction (*) between two predictors - MATRIX!
###
```{r}
fit_list3 <- list()  # Initialize an empty list to store the models
model3 <- list() # Initialize an empty list to store combined models
loo_auto3 <- list()  # Initialize an empty list to store LOO scores
model3_output_bind <- tibble()      # Initialize an empty dataframe for final table results

# prevent pop-up windows/questions
options(buildtools.check = function(action) TRUE)

# Run fit on loop - not combining (combine = FALSE), so that you can extract the LOO for each run later, combined using combined_models()
for (param in parameters_model2) {
for (param2 in combined_parameters) {
  # Construct the formula dynamically
  formula3 <- formula(paste("log10_sxtA_Copies_mL_BDL_Replaced | cens(sxtA_Copies_mL_censored) ~", param, "*", param2))
  
  # Run brm_multiple 
  fit_imp3 <- brm_multiple(formula3, data = imp1b_short, chains = 4, warmup = 1000, iter = 2000, combine = FALSE)
  
  # Write out equation
  equation <- paste0(param, "_interaction_", param2)
  
  # Store the individual model in the list (backup)
  fit_list3[[equation]] <- fit_imp3
  
  # Combine the model into object
  model3[[equation]] <- combine_models(mlist = fit_imp3, check_data = FALSE)

  # Get LOO for the combined model
  loo_auto3[[equation]] <- brms::loo(model3[[equation]])

#Compile:
#Intercept: Estimate, Estimate Error, l-95% CI, u-95% CI, Rhat, Bulk_ESS, Tail_ESS
#Parameter: Estimate, Estimate Error, l-95% CI, u-95% CI, Rhat, Bulk_ESS, Tail_ESS
#R-squared

#Generate summary (for loop)
summary_result3 <- summary(model3[[equation]])
r2 <- bayes_R2(model3[[equation]])
# Extract R-squared value
param_r2 <- r2[1]

# Extract model results
fixed_effects_matrix <- summary_result3$fixed

# Convert the fixed effects to a tibble
fixed_effects <- as_tibble(fixed_effects_matrix)

# Add the parameter names as a new column
fixed_effects <- fixed_effects %>%
  add_column(Parameter = equation,
             Row = rownames(fixed_effects_matrix), .before = 1,
             R_squared = param_r2,
             Model_formula = paste("log10_sxtA_Copies_mL_BDL_Replaced | cens(sxtA_Copies_mL_censored) ~", param, "*", param2))

model3_output_bind <- bind_rows(model3_output_bind, fixed_effects)
}
}

# View the final dataframe
model3_output <- print(model3_output_bind) %>%
                        arrange(-R_squared)

#Save objects
saveRDS(model3, file="qPCR/model3_June21_24.RData")
saveRDS(loo_auto3, file="qPCR/loo_auto3_June21_24.RData")
write_csv(model3_output, "qPCR/model3_output_June21_24.csv")
#This concludes the second iteration of linear models, once again if rhat >1.01
model3_output <- read_csv("qPCR/model3_output_June21_24.csv")

View(model3_output)
```

###
###Model4: Let's do loop for (+) three predictors - MATRIX!
###
```{r}
#Select best parameters
parameter1_model4 <- "Comb_Temperature_C"
parameter2_model4 <- "log10_Ammonia_ug_N_L_Replaced"

#remove temp and ammonia from combined_parameters
combined_parameters_m4 <- combined_parameters[!combined_parameters %in% c("Comb_Temperature_C", "log10_Ammonia_ug_N_L_Replaced")]

fit_list4 <- list()  # Initialize an empty list to store the models
model4 <- list() # Initialize an empty list to store combined models
loo_auto4 <- list()  # Initialize an empty list to store LOO scores
model4_output_bind <- tibble()      # Initialize an empty dataframe for final table results

# prevent pop-up windows/questions
options(buildtools.check = function(action) TRUE)

# Run fit on loop - not combining (combine = FALSE), so that you can extract the LOO for each run later, combined using combined_models()
for (param2 in combined_parameters_m4) {
  # Construct the formula dynamically
  formula4 <- formula(paste("log10_sxtA_Copies_mL_BDL_Replaced | cens(sxtA_Copies_mL_censored) ~", parameter1_model4, "+", parameter2_model4, "+", param2))
  
  # Run brm_multiple 
  fit_imp4 <- brm_multiple(formula4, data = imp1b_short, chains = 4, warmup = 1000, iter = 2000, combine = FALSE)
  
  # Store the individual model in the list (backup)
  fit_list4[[paste(parameter1_model4, "+", parameter2_model4, "+", param2)]] <- fit_imp4
  
  # Combine the model into object
  model4[[paste(parameter1_model4, "+", parameter2_model4, "+", param2)]] <- combine_models(mlist = fit_imp4, check_data = FALSE)

  # Get LOO for the combined model
  loo_auto4[[paste(parameter1_model4, "+", parameter2_model4, "+", param2)]] <- brms::loo(model4[[paste(parameter1_model4, "+", parameter2_model4, "+", param2)]])

#Compile:
#Intercept: Estimate, Estimate Error, l-95% CI, u-95% CI, Rhat, Bulk_ESS, Tail_ESS
#Parameter: Estimate, Estimate Error, l-95% CI, u-95% CI, Rhat, Bulk_ESS, Tail_ESS
#R-squared

#Generate summary (for loop)
summary_result4 <- summary(model4[[paste(parameter1_model4, "+", parameter2_model4, "+", param2)]])
r2 <- bayes_R2(model4[[paste(parameter1_model4, "+", parameter2_model4, "+", param2)]])
# Extract R-squared value
param_r2 <- r2[1]

# Extract model results
fixed_effects_matrix <- summary_result4$fixed

# Convert the fixed effects to a tibble
fixed_effects <- as_tibble(fixed_effects_matrix)

# Add the parameter names as a new column
fixed_effects <- fixed_effects %>%
  add_column(Parameter = paste(parameter1_model4, "+", parameter2_model4, "+", param2),
             Row = rownames(fixed_effects_matrix), .before = 1,
             R_squared = param_r2,
             Model_formula = paste("log10_sxtA_Copies_mL_BDL_Replaced | cens(sxtA_Copies_mL_censored) ~", parameter1_model4, "+", parameter2_model4, "+", param2))

model4_output_bind <- bind_rows(model4_output_bind, fixed_effects)
}


# View the final dataframe
model4_output <- print(model4_output_bind) %>%
                        arrange(-R_squared)

#Save objects
saveRDS(model4, file="qPCR/model4_June18_24.RData")
saveRDS(loo_auto4, file="qPCR/loo_auto4_June18_24.RData")
write_csv(model4_output, "qPCR/model4_output_June18_24.csv")
#This concludes the second iteration of linear models, once again if rhat >1.01
model4_output <- read_csv("qPCR/model4_output_June18_24.csv")

View(model4_output)

```

Combine loo files to do final model comparison
```{r}

model1_loo  <- readRDS(file="qPCR/loo_auto_model1_June12_24.RData")
model1b_loo <- readRDS(file="qPCR/loo_auto1b_June12_24.RData")
model1c_loo <- readRDS(file="qPCR/loo_auto1c_June13_24.RData")
model2_loo  <- readRDS(file="qPCR/loo_auto2_June17_24.RData")
model3_loo  <- readRDS(file="qPCR/loo_auto3_June21_24.RData")
model4_loo  <- readRDS(file="qPCR/loo_auto4_June18_24.RData")

loo_bind <- c(model1_loo, model1b_loo, model1c_loo, model2_loo, model3_loo)

loo_comp <- loo_compare(loo_bind)
View(loo_comp)

```

```{r}

model1_read <- readRDS(file="qPCR/model1_June12_24.RData")
model1b_read <- readRDS(file="qPCR/model1b_June12_24.RData")
model1c_read <- readRDS(file="qPCR/model1c_June13_24.RData")
model2_read <- readRDS(file="qPCR/model2_June17_24.RData")
model3_read <- readRDS(file="qPCR/model3_June21_24.RData")
model4_read <- readRDS(file="qPCR/model4_June18_24.RData")

summary(model1b_read[["log10_Ammonia_ug_N_L_Replaced"]])
summary(model1_read[["Comb_Temperature_C"]])
summary(model2_read[["log10_Ammonia_ug_N_L_Replaced + Comb_Temperature_C"]])
summary(model2_read[["log10_Ammonia_ug_N_L_Replaced_Comb_Temperature_C"]])
summary(model3_read[["Comb_Temperature_C_interaction_log10_Ammonia_ug_N_L_Replaced"]])
View(model3_output)

```

